Exponential Integrators for PDEs arising in meteorology

### 2024-09-12 article_4.tex
Spelling Corrections

\subsection{Numerical Results}
Here we run numerical experiments, computing $e^Av$ for a tridiagonal matrix $A$ of sizes $131072$ and $524288$, where $A$ is a triagonal matrix with $2n^2$ along the diagonal and $-n^2$ along the upper and lower diagonals. We will compare the methods with respect to computation time, error and size of the Kyrlov subspace. Here, the error is computed as the Euclidian distance between the Scipy method and the Krlob subspace method that is being tested.

>>>>

\subsection{Numerical Results}
Here we run numerical experiments, computing $e^Av$ for a tridiagonal matrix $A$ of sizes $131072$ and $524288$, where $A$ is a tridiagonal matrix with $2n^2$ along the diagonal and $-n^2$ along the upper and lower diagonals. We will compare the methods with respect to computation time, error and size of the Kyrlov subspace. The error is computed as the Euclidian distance between Scipy and the Krlov subspace method being tested.
